%-------------------------
% Resume in Latex
% Author : Sashwat K
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\pagestyle{fancy}
\fancyhf{} 

%-------------------------
% clear all header and footer fields
%-------------------------

\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-------------------------
% Adjust margins
%-------------------------

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Sections formatting
%-------------------------

\titleformat{\section} {
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
%-------------------------

\newcommand{\resumeItem}[2]{
	\item\small{
    		\textbf{#1}{: #2 \vspace{-2pt}}
  	}
}

\newcommand{\resumeSubheading}[4]{
  	\vspace{-1pt}\item
    	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      		\textbf{#1} & #2 \\
      		\textit{\small#3} & \textit{\small #4} \\
    	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  	\textbf{\href{https://sashuu6.github.io/}{\Large Sashwat K}} & Email : \href{mailto:sashwat0001@gmail.com}{sashwat0001@gmail.com}\\
  	\href{https://sashuu6.github.io/}{sashuu6.github.io} , \href{https://sashwat.in/}{sashwat.in}& Mobile : +91 8281962557 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  	\resumeSubHeadingListStart
    		\resumeSubheading
      			{College of Engineering Trivandrum (CET)}{Thiruvananthapuram, India}
     	 		{Post Graduation; Masters in Computer Application}{August. 2017 -- April. 2020}
    		\resumeSubheading
     			 {Christ Nagar College}{Thiruvananthapuram, India}
      			{Graduation; Bachelor in Computer Application}{June. 2014 -- May. 2017}
    		\resumeSubheading
      			{Kendriya Vidyalaya AirForce Station Akkulam}{Thiruvananthapuram, India}
      			{High School; Computer Science}{April. 2012 -- March. 2014}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  	\resumeSubHeadingListStart
  	\resumeSubheading
      		{TechWithUs PVT LTD}{CET, Thiruvananthapuram}
      		{Software Developer}{March 2019 - Present}
      		\resumeItemListStart
			\resumeItem{About}
				{A Startup of CET that developed softwares for KTU and the college.}
        			\resumeItem{ExamMarker}
          			{ExamMarker is a product developed using python, electron, javascript, Web and PHP. I contributed in developing the sections that used python, electron and javascript.}
      		\resumeItemListEnd
    	\resumeSubheading
      		{Appfabs PVT LTD}{Technopark, Thiruvananthapuram, India}
      		{Intern}{May 2018 - September 2018}
      		\resumeItemListStart
        			\resumeItem{Cyber security}
          			{Cybersecurity is the protection of internet-connected systems, including hardware, software and data, from cyberattacks. In a computing context, security comprises cybersecurity and physical security -- both are used by enterprises to protect against unauthorised access to data centres and other computerised systems.}
      		\resumeItemListEnd
		\resumeSubheading
      		{IoT Lab}{CET, Thiruvananthapuram}
      		{Student faculty}{September 2017 - April 2018 \& October2018 - January 2019}
      		\resumeItemListStart
        			\resumeItem{Arduino UNO}
          			{The Arduino UNO is an open-source micro-controller board based on the Microchip ATmega328P micro-controller and developed by Arduino.cc. As a member of student faculty, I was given the chance to take classes on Arduino UNO to the students of CET.}
        			\resumeItem{Raspberry Pi}
          			{The Raspberry Pi is a tiny and affordable computer that can be used for practical projects and to learn programming. I took workshops on Raspberry Pi.}
      		\resumeItemListEnd
  	\resumeSubHeadingListEnd

%-----------Workshops Handled-----------------
\section{Workshops Handled}
  	\resumeSubHeadingListStart
    		\resumeSubheading
     			{Raspberry Pi Workshop}{CET, Thiruvananthapuram}
      			{IOT Lab}{2018}
      			\resumeItemListStart
       				 \resumeItem{Python}
          				{This workshop was conducted by a team of 4 students including me. In this workshop, I handled python session.}
      			\resumeItemListEnd
      		\resumeSubheading
      			{Arduino Workshop}{CET, Thiruvananthapuram}
     			{IOT Lab}{2018}
      			\resumeItemListStart
        				\resumeItem{Arduino}
          				{This workshop covered all the sections from Arduino basics, embedded C, micro controller vs micro processor and few basic programs.}
     	 		\resumeItemListEnd
      		\resumeSubheading
     		 	{Beaglebone Workshop}{CET, Thiruvananthapuram}
      			{IOT Lab}{2018}
      			\resumeItemListStart
        				\resumeItem{Linux and Python}
          				{This workshop was conducted by a team of 4 students including me. In this workshop, I handled Linux and Python session.}
      			\resumeItemListEnd
      		\resumeSubheading
      			{Raspberry Pi Workshop}{CET, Thiruvananthapuram}
     			{Drishti}{2018}
      			\resumeItemListStart
        				\resumeItem{Pi}
          				{This workshop was conducted at Drishti (Technical Fest, CET). The session included about introduction Raspberry Pi, Linux, working remotely, Python, creating Pi server and home automation using Pi.}
      			\resumeItemListEnd
      		\resumeSubheading
     			 {Git Workshop}{Muthoot Institute of Technology and Science, Kochi}
      			{}{2019}
     	 		\resumeItemListStart
        				\resumeItem{Git}
          				{In this workshop, I took session on Git and Github.}
      			\resumeItemListEnd
 	 \resumeSubHeadingListEnd

%-----------Achievements-----------------
\section{Achievements}
  	\resumeSubHeadingListStart
		\resumeSubheading
      			{HacktoberFest}{DigitalOcean and GitHub}
      			{Pull Requests}{October 2018 \& 2019}
			\resumeItemListStart
      				\resumeItem{}
          				{Online Event}
       			\resumeItemListEnd
		\resumeSubheading
      			{Ignite' 19}{NIT Suratkal}
      			{All India MCA Meet}{October 2019}
			\resumeItemListStart
      				\resumeItem{Nexus - 1st prize}
          				{Non - Technical, Team event - 5 members}
       			\resumeItemListEnd
		\resumeSubheading
      			{Version' 19}{NIT Tiruchirappalli}
      			{All India MCA Meet}{September 2019}
			\resumeItemListStart
      				\resumeItem{Technothon - 1st prize}
          				{Project presentation event. (Individual event)}
				\resumeItem{Pheonix - 1st prize}
          				{Interview competition for KLA's Internship. The participants are selected based on their overall performance in the whole event. (Individual event)}
				\resumeItem{Star Performer}
          				{Given for best performance in the 2 day event.}
       			\resumeItemListEnd
   		\resumeSubheading
      			{Nakshatra' 19}{NIT Calicut}
      			{All India MCA Meet}{February 2019}
			\resumeItemListStart
      				\resumeItem{Quibble - 1st prize}
          				{Non - Technical quiz, Team event - 2 members}
				\resumeItem{Enigma - 2nd prize}
          				{Technical quiz, Team event - 2 members}
       			\resumeItemListEnd
  	\resumeSubHeadingListEnd

%-----------MY PROJECTS-----------------
\section{My Projects}
  	\resumeSubHeadingListStart
    		\resumeSubItem{3-factor-authenticated-door-lock}
      			{ A 3 factor authenticated door lock using Atmega328p, 74HC595 multiplexer, key switch, keypad and RFID. This project is available at \url{https://github.com/sashuu6/3-factor-authenticated-door-lock}.}
    		\resumeSubItem{digital-clock-with-birthday-alarm}
      			{The digital clock with birthday alarm is a DYI alarm built using Arduino UNO, Adafruit OLED and DS 3231 RTC module. This project is available at \url{https://github.com/sashuu6/digital-clock-with-birthday-alarm}.}
      		\resumeSubItem{vOne}
      			{My version of Arduino Uno for board isolation. This project is available at \url{https://github.com/sashuu6/vOne}.}
       		\resumeSubItem{Realtime Barcode Scanner}
      			{My version of Barcode Scanner developed using Python and OpenCV. This project is available at \url{https://github.com/sashuu6/realtime-barcode-scanner}.}
		\resumeSubItem{Python Fingerprint Recognition}
			{In this contributed project, I have fixed the python errors due to which the program doesn't run. Parent project-\url{https://github.com/kjanko/python-fingerprint-recognition}. My project-\url{https://github.com/sashuu6/python-fingerprint-recognition}.}
  	\resumeSubHeadingListEnd

  
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  	\resumeSubHeadingListStart
    		\item{
      			\textbf{Languages}{: C, Python, ElectronJS, AngularJS, Bash }
      			\hfill
      			\textbf{Technologies}{: Git, Linux, Docker}
    		}
		\item{
      			\textbf{Softwares}{: Visual Studio Code, Arduino IDE}
      			\hfill
      			\textbf{Design Tools}{: Fritzing, Fusion 360}
    		}
  	\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
